Appendix

### 2019-12-03 figures/07_model-selection.Rmd
add coefficient summary tables, closes #25

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tp,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
  mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)
```

@@

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tn,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
  mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)
```

>>>>

gg_tp <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tp,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
  mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

# compute posterior standard deviations
gg_tp_sd <- spread_draws(fit_tp, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    round(sd(value), 2)))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  setNames(c("pretty", "sd"))

write.csv(
  left_join(
    dplyr::select(gg_tp, -matches("X")), 
    gg_tp_sd), 
          "../data/gg_tp.csv", row.names = FALSE)
```

@@

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    quantile(value, probs=c(0.05,0.5,0.95))))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  dplyr::bind_rows(
    dplyr::select(re_global[best_tn,], -term, -response), 
    data.frame(pretty = "", `5%` = "", `50%` = "", `95%` = "", 
               stringsAsFactors = FALSE)
    ) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0)) %>%
  left_join(dplyr::select(pred_key, pretty, category)) %>%
  mutate(category = tidyr::replace_na(category, "Land-use cover")) %>%
  mutate(category = factor(category, 
                           levels = rev(c("Nutrient inputs", "Nutrient transport", 
                                      "Buffer configuration", "Lake", 
                                      "Land-use cover")))) %>%
  mutate(category = forcats::fct_recode(category, 
                                        Buffer = "Buffer configuration", 
                                        LULC = "Land-use cover")) %>%
  arrange(category) %>%
  ungroup() %>% distinct(pretty, .keep_all = TRUE) %>%
  mutate(pretty = factor(pretty, levels = pretty)) %>%
  arrange(category, pretty)

# compute posterior standard deviations
gg_tn_sd <- spread_draws(fit_tn, `b_.*`, regex = TRUE) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  dplyr::filter(key != "b_Intercept") %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  group_by(pretty) %>%
  summarize(value = list(tibble::enframe(
    round(sd(value), 2)))) %>% unnest() %>%
  tidyr::spread(name, value) %>%
  setNames(c("pretty", "sd"))

write.csv(
  left_join(
    dplyr::select(gg_tn, -matches("X")), 
    gg_tn_sd), 
          "../data/gg_tn.csv", row.names = FALSE)
```

### 2019-12-03 manuscript/appendix.Rmd
add coefficient summary tables, closes #25

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = log(ag), y = log(tn))) + 
  ylab("TN (ug/L)") +
  xlab("Percent Agriculture"), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) +
  ylab("TP (ug/L)") +
  xlab("Percent Agriculture")
)

@@

>>>>

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = log(ag), y = log(tn))) + 
  ylab("log(TN) (ug/L)") +
  xlab("log(Percent Agriculture)"), 
ggplot(data = dt) + 
  geom_point(aes(x = log(ag), y = log(tp))) +
  ylab("log(TP) (ug/L)") +
  xlab("log(Percent Agriculture)")
)

@@

```{r coef-summary-table}
gg_tp <- read.csv("../data/gg_tp.csv", stringsAsFactors = FALSE) %>%
  dplyr::filter(nchar(pretty) > 0) %>%
  dplyr::select(-signif, -category) %>%
  setNames(c("variable", "5%", "50%", "95%", "SD")) %>%
  mutate_if(is.numeric, function(x) round(x, 2))
gg_tn <- read.csv("../data/gg_tn.csv", stringsAsFactors = FALSE) %>%
  dplyr::filter(nchar(pretty) > 0) %>%
  dplyr::select(-signif, -category) %>%
  setNames(c("variable", "5%", "50%", "95%", "SD")) %>%
  mutate_if(is.numeric, function(x) round(x, 2))

knitr::kable(gg_tp, caption = "Coefficient summaries for top-ranked TP model.")

knitr::kable(gg_tn, caption = "Coefficient summaries for top-ranked TN model.")
